---
title: "Regression"
author: "Anna Yeaton"
date: "Fall 2019"
output:
  html_document:
    df_print: paged
fontsize: 11pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = T)
```

# Lab Section

In this lab, we will go over regression. We will be using the caret package in R. https://topepo.github.io/caret/train-models-by-tag.html

# Perfomance Metrics 

## Residual 

Deviation of the observed value to the estimated value (sample mean)
$$residual=y_i - \hat{y_i}$$
where $\hat{y_i}$ is the estimated value

## Mean Squared Error (MSE)

$$MSE=\frac{1}{n}\sum_{i=1}^{n}(y_i - \hat{y_i})^2$$

## Root Mean Squared Error (RMSE)
Same units as original data.

$$RMSE=\sqrt{MSE}$$

## L2 regularization : Ridge regression. Regularize by adding the sum of the coefficients, squared, to the function. 

$$Ridge Regression=\sum_{i=1}^{n}(y_i - w_0 - \sum_{j=1}^{p}w_jx_{ij})^2 + \lambda\sum_{j=1}^p(w_j)^2$$

## L1 regularization : Lasso Regression. Regularize by adding the sum of the absolute value of the coefficients to the model. Coefficient estimates may be pushed to zero -- Lasso can perform variable selection

$$Lasso Regression=\sum_{i=1}^{n}(y_i - w_0 - \sum_{j=1}^{p}w_jx_{ij})^2 + \lambda\sum_{j=1}^p|w_j|$$


\newpage

### The broad steps of Machine learning in R. 

1. Split the data into training and test. Set test aside. 

2. Fit a good model to the training data. 

3. See how your model did on the training data.

4. Test how your model performs on the test data. 

# Regression

```{r, include=FALSE}
library(caret)
library(MASS)
library(ggplot2)
library(dplyr)
library(ggfortify)
library(glmnet)

#Mauna Loa CO2 concentrations
data(airquality)
```


1. Split data into training and test set (75% in train set, 25% in test set)

```{r}
#Randomly split data into sets
tmp = sample(1:153,153,replace=F)
airquality = airquality[c(tmp),]
train_regression = airquality[1:114,]
test_regression = airquality[115:153,]
```


### Linear Regression

* Assumes a linear relationship. 
* Independent variables should not be correlated (no mulitcollinearity)
* The number of observations should be greater than the number of independent variables.


$$RSS=\sum(y_i - \hat{y_i})^2$$
We will predict the response of the Temperature based on Wind. 

This is the data we will fit a linear model to. 
```{r}
ggplot(data = train_regression) +
geom_point(aes(x=Wind, y=Temp)) +
theme_bw()
```

2. Create and fit a linear model to predict Temperature from Wind using the training set

```{r}
#help(train)

linear_regression <- train( Temp~Wind , data=train_regression, method = "lm")
```


3. Vizualize how your model performed on the train data by plotting the regression line on top of the train data points. 
```{r}
ggplot(data = train_regression) +
  geom_point(aes(x=Wind, y=Temp)) +
  geom_line(aes(x=Wind, y=Wind*linear_regression$finalModel$coefficients[2]+linear_regression$finalModel$coefficients[1])) +
  theme_bw()
```


4. Explore how the model performs on the test data. For Linear Regression:

* The residuals should be close to zero.
* There should be equal variance around the regression line (homoscedasticity).
* Residuals should be normally distributed.
* Independent variables and residuals should not be correlated.

4 a) See how the model performs on the test data
```{r}
#help(predict)
linear_predict <- predict(linear_regression, newdata=test_regression)
```

4 b) Look at the residuals. Are they close to zero?
```{r}
#look at the median residual value. Close to zero is best
#help(summary)
summary(linear_predict)
```


4 c) Plot predicted temperature vs observed temperature. A strong model should show a strong correlation
```{r}
plot(linear_predict,test_regression$Temp,xlab="Predicted values",ylab="Real values")
cor.test(linear_predict,test_regression$Temp)
#r=0.49, p=0.0014, the model is relatively valid.
```

4 d) Visualize the predicted values in relation to the real data points. Look for homoscedasticity
```{r}
# Extract coefficients from the model
lm_coef = linear_regression$finalModel$coefficients

# plot the regression line on the predicted values
ggplot(data = test_regression) +
  geom_point(aes(x=Wind, y=linear_predict)) +
  geom_line(aes(x=Wind, y=lm_coef[1]+Wind*lm_coef[2])) +
  ylab("Predicted values") + 
  theme_bw()

# plot the original test values
ggplot(data = test_regression) +
  geom_point(aes(x=Wind, y=Temp)) +
  geom_line(aes(x=Wind, y=lm_coef[1]+Wind*lm_coef[2])) +
  ylab("Real values in test set") +
  theme_bw()
```

4 e) Residuals should be normally distributed. Plot the density of the residuals
```{r}
residuals_lin <- residuals(linear_regression)

ggplot() + geom_density(aes(residuals_lin)) + xlab("Model residuals")
```


4 f) Independent variables and residuals should not be correlated
```{r}
cor.test(train_regression$Wind, resid(linear_regression))
#the insignificant p value shows that IV and residuals are not correlated
```


### Linear Regression with Regularization

5. Create a linear model using L1 or L2 regularization to predict Temperature from Wind and Month variables. Plot your predicted values and the real Y values on the same plot. 

```{r}
lambda_seq = 10^seq(1, -3, by = -.1)
IVs_train = as.matrix(select(train_regression,3,5))
IVs_test = as.matrix(select(test_regression,3,5))

cv_out = cv.glmnet(IVs_train, train_regression$Temp, alpha = 1, lambda = lambda_seq)

best_lambda = cv_out$lambda.min

lasso_model = glmnet(IVs_train, train_regression$Temp, alpha = 1, lambda = best_lambda)

lasso_predict = predict(lasso_model, newx = IVs_test, s = best_lambda)

ggplot(data = test_regression,aes(x=Wind)) +
  geom_point(aes(y=Temp)) +
  geom_point(aes(y=lasso_predict),col="red") +
  xlab("Wind") + ylab("Temperature")
  
ggplot(data = test_regression,aes(x=Month)) +
  geom_point(aes(y=Temp)) +
  geom_point(aes(y=lasso_predict),col="red") +
  xlab("Wind") + ylab("Temperature")

cor.test(lasso_predict,test_regression$Temp)
#r=0.58, p<.001, the model is pretty good!
```

